Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Small tweak to wording.

\subsubsection{Comprehension Questions}
Because participants might be biased to specific devices or companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable device. Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which would be the basis for all questions on wearable computing risks. We highlighted the capabilities of this device and described several use cases. To ensure that participants had read and understood this device's capabilities, we presented them with two multiple-choice comprehension questions.

>>>>

\subsubsection{Comprehension Questions}
Because participants might be biased to specific devices or companies (e.g., visceral reactions to Google Glass based on popular media stories), we based our questions on a fictitious wearable device. Thus, the beginning of the survey introduced participants to the ``Cubetastic3000,'' which was the basis for all questions on wearable computing risks. We highlighted the capabilities of this device and described several use cases. To ensure that participants had read and understood this device's capabilities, we presented them with two multiple-choice comprehension questions.
